Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Add univariate param density figure

library(hector.permafrost.emit) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

@@

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}
```

@@

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
knitr::include_graphics(file_in(here::here("analysis", "figures", "global_draws.png")))
```

@@

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_biome_sims)
knitr::include_graphics(file_in(here::here("analysis", "figures", "biome_draws.png")))
```

@@

>>>>

library(hector.permafrost.emit)

@@

f <- function(...) {
  here::here("analysis", "figures", ...)
}
```

@@

These distributions are also shown in Figure 1.

```{r param-density, echo = FALSE, fig.cap = param_density_cap}
param_density_cap <- paste(
  "Input parameter distributions for this analysis."
)
knitr::include_graphics(file_in(f("param-density.png")))
```

`r mdcap(param_density_cap)`

@@

@@

`r mdcap(global_sensitivity_cap)`

@@

@@

# Appendix

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
knitr::include_graphics(file_in(f("global_draws.png")))
```

`r mdcap(global_dist_cap)`

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for Hector with biomes."
)
# readd(draws_biome_sims)
knitr::include_graphics(file_in(fig("biome_draws.png")))
```

`r mdcap(biome_dist_cap)`
